High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-23 doc/asplos2013/results.tex

Figure~\ref{fig:bulksync} compare
the performance of the bulk-synchronous implementations versus the original
implementations for Circuit, Fluid, and AMR respectively.  Each plot contains
performance curves for both implementations on two different problem sizes.
Circuit is a compute-bound application and the bulk-synchronous implementation
performs reasonably well.  By 16 nodes however the overhead grows to 19\%
and 22\% on the small and large inputs respectively.  The Fluid application 
has a more evenly balanced computation-to-communication ratio.  As a result,
Fluid performance suffers significantly more by switching to
a bulk-synchronous model.  At 16 nodes, performance is 135\% and 52\% worse
than the original Legion implementations on the small and large problem sizes
respectively.  Finally, the AMR application is a memory bound application, and on 16 nodes
the bulk-synchronous version is 82\% and 102\% slower on the small and
large problem sizes.

>>>>

Figure~\ref{fig:bulksync} compares
the performance of the bulk-synchronous implementations versus the original
implementations for Circuit, Fluid, and AMR respectively.  Each plot contains
performance curves for both implementations on two different problem sizes.
Circuit is a compute-bound application and the bulk-synchronous implementation
performs reasonably well.  By 16 nodes however the overhead grows to 19\%
and 22\% on the small and large inputs respectively.  The Fluid application 
has a more evenly balanced computation-to-communication ratio.  As a result,
Fluid performance suffers significantly more by switching to
a bulk-synchronous model.  At 16 nodes, performance is 135\% and 52\% worse
than the original Legion implementations on the small and large problem sizes
respectively.  Finally, the AMR application is a memory bound application, and on 16 nodes
the bulk-synchronous version is 82\% and 102\% slower on the small and
large problem sizes.
